FictionEro - Data Cleaning

### 2024-06-26 analysis/1_cleaning.qmd
minor

>>>>

```{r}
#| warning: false

dat <- df |> 
  select(starts_with("GAAIS"), starts_with("BAIT")) |> 
  select(matches("[[:digit:]]"))

ega <- EGAnet::EGA(
        data = dat,
        seed=123,
        model="glasso",
        algorithm="leiden",
        plot.EGA=FALSE,
        verbose=FALSE)

plot(ega)

plot(parameters::factor_analysis(dat, n=6, rotation="oblimin", sort=TRUE))
```

```{r}
#| eval: false
#| echo: false

# Used for feedback screen in the new BAIT implementations
mean(rowMeans(df[c("GAAIS_Positive_12", "GAAIS_Positive_17")]))
```
